% preamble adapted from https://math.duke.edu/sites/math.duke.edu/files/CV.tex

\documentclass[12pt,letterpaper]{article}
\oddsidemargin=.15in
\evensidemargin=.15in
\textwidth=6in
\topmargin=-.5in
\textheight=9in
\parindent=0in

\pagestyle{empty}

\begin{document}

\frenchspacing

\begin{center}
Bennett E. Todd III

\textless bet@rahul.net\textgreater

\textless bennett.e.todd@gmail.com\textgreater

(201) 667-2368
\end{center}

\section*{Languages and Systems}

I am expert in Perl and Bourne Shell. I know the C programming
language well. I've studied perl 6 and rust. I've designed and
negotiated security policies, built and maintained firewalls and IDS
systems, and performed security administration. I support Red Hat
Linux regularly, and work occasionally with Solaris. My focus is
Unix system administration automation and security.

\section*{Papers and Projects}

I've published a paper on auditing firewalls, available from

\textless URL:http://bet.github.io/firewall-audit-paper/p5.htm\textgreater.

I've written and maintained several open source projects, including
a high-performance POP-before-SMTP authentication daemon for use
with Postfix, and a custom Linux distribution based on embedded
Linux.

I've written an overview of cryptography,

\textless URL:http://bet.github.io/crypto/index.html\textgreater

\section*{Experience}

TD Securities \hfill New York, NY
2016-2018

I helped in adding DMARC, DKIM, and SPF records for email security.
I helped document and simplify our administration procedures for
our multi-factor authentication servers, and enable their use, via
RADIUS, for a password archive; and created operations documentation
for upgrading them. I helped evaluate Content Distribution Network
and Web Application firewall vendors. I wrote and deployed programs
to automatically transfer user account lists, with roles, from two
different vendor systems to an in-house account re-authorization
system.
\\~

CNBC \hfill Englewood Cliffs, NJ
2013-2014

I built an IDS sensor, did post-incident forensic analysis, and
created our password policy. I built and deployed a tool for
forensic session logging, as a companion to the IDS sensor. I
designed our configuration collection and tracking system.
\\~

Goldman Sachs \hfill New York, NY
2008-2010

I helped automate system administration of Linux and Solaris
servers, including automated periodic inventory of systems and batch
system modification.
\\~

Morgan Stanley \hfill New York, NY
2003-2008

I was a Unix systems engineer at Morgan Stanley. I created
and supported their secure Linux build, for stand alone and
security-sensitive applications. I maintained and developed their
internal DNS infrastructure. I designed the DNS architecture and
servers for a new, highly scalable internal build based on CERN's
Quattor.
\\~

Soci\'{e}t\'{e} G\'{e}n\'{e}rale \hfill New York, NY
2002-2003

I was a security analyst at Soci\'{e}t\'{e} G\'{e}n\'{e}rale, in
their Information Security and Governance department. I designed and
implemented their Perimeter Intrusion Detection System; I created
several utilization reporting systems, importing logs of various
sorts --- web utilization, NT and Unix login activity --- and
web-based query/reporting tools for viewing the data.
\\~

Morgan Stanley \hfill New York, NY
2001-2002

I was a security analyst at Morgan Stanley, in their Information
Technology Security Engineering department. I designed and
implemented their virus-scanning bastion email server. I developed
and implemented a remote computing solution for ssh access. I
supported many groups, reviewing designs and auditing code,
helping ensure that new deployments introduced no security
problems.
\\~

Oven Digital \hfill New York, NY
1999-2000

I was the senior security and systems analyst at Oven Digital.

I wrote their security policy, and designed and implemented their
firewalls. I set up their email server and DNS infrastructure,
and developed the email content filtering that trapped out
any email worms before they are delivered to their users. I
provided the architectural design and implementation for scalable,
high-performance, high-security, high-availability web server farms.
\\~

Lehman Brothers, Inc. \hfill Jersey City, NJ
1998-1999

I was a Senior Systems Administrator and Systems Analyst at Lehman
Brothers.

I developed a full-text index search engine companion to the
in-house trouble ticket database; I developed a data mining
application for systems management, that collected information both
from direct probes of systems, and from various administrative
tables in management databases, and allowed report generation
queries through a web interface against the collected data. This was
instrumental in planning and managing upgrades.
\\~

Fuji Capital Markets Corp. \hfill New York, NY
1995-1998

I was a Senior Systems Analyst at Fuji Capital Markets.

I worked as a Systems Administrator, with a team that supported 200
users. I was also the security administrator, charged with internal
and external computer systems security planning, maintenance,
testing, and reporting. I designed the Jumpstart configuration
for Solaris, along with the packaging standard and automounter
architecture we used for installing and accessing software.
\\~

Salomon Brothers, Inc. \hfill New York, NY
1991-1995

I worked as a Senior Systems Analyst for SBI.

I set up an in-house WWW server, designed our web documents,
and put the Perl 5 manual up for access via WWW, with an
automatically-maintained index of all the documentation for
libraries.

I headed up the design and implementation of facilities for
automating the installation, restoration (e.g. after disk failure),
and maintenance of several hundred workstations. I produced a
software suite for automated network load of SunOS 4.x, much in the
style of Jumpstart. The group I worked with provided second-tier
support for some seventy System Administrators, who were in turn
responsible for machines serving roughly a thousand end-users,
including traders, researchers, and application developers.

I brought in, built, and supported substantial free software
packages, including \TeX and \LaTeX, Xfig and Transfig, X11R5, Perl,
TCL/Tk, and all the GNU software. I wrote software and performed
delivery testing in support of deploying software into production. I
dramatically enhanced the local software distribution process, both
by writing software and by establishing standards for packaging and
delivery.

I tested and packaged many security-related facilities, including
net-distributed security challenge programs like Crack, COPS, and
SATAN, as well as security fixes like Sun's ypserv patch and new
versions of sendmail.
\\~

Radiology Department, Duke University Medical Center \hfill Durham, NC
1988-1991

My responsibilities included system administration, user support,
system programming, and application programming on a network of Sun
workstations and other systems, used for medical image processing. I
completed two substantial tasks connecting non-standard peripherals
to our system, requiring system programming. I performed security
auditing, and improved the network's security substantially.
\\~

Computation Center, Duke University \hfill Durham, NC
1984-1988

I supported System V UNIX on AT\&T 3B5, IBM OS/MVS and VM on various
mainframes, and MS-DOS on PCs. In this job I answered questions from
users all over the University, performed minor contract programming
tasks, and served as system administrator for the UNIX facility
offered by the Computation Center.
\section*{Education}
Department of Electrical Engineering, School of Engineering, Durham, NC
1980-1984 \hfill Duke University

I earned a Bachelor of Science in Electrical Engineering, Magna
Cum Laude, and completed departmental requirements for a Bachelor
of Science in Computer Science.
\end{document}
